Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-08-02 doc/PRF2022/PRF_main.tex

\section{Introduction}
% Put \label in argument of \section for cross-referencing
%\section{\label{}}
Janus particles are colloids whose surfaces 
%have different properties. For example, it is common for the surface of a Janus
%particle to be 
may be partly hydrophilic and hydrophobic (polar and non-polar).
More generally the surface of a Janus particle may have a spatial distribution of hydrophobicity/hydrophilicity.
In a viscous solvent, in a quiescent flow, Janus particles often self-assemble into
structures with tunable functions for biomedical engineering
applications~\cite{GheisariSahfieeAbbasiEtAl2021_DMR,
LiuYangHuangEtAl2016_Angew, LiWangYaoEtAl2019_Nanoscale, Bradley2016}.
Depending on the interactions between Janus particles (JPs) and the
surrounding viscous solvent, JPs self-assemble into oligomers of various
geometries and sizes~\cite{Bradley2017}.

Dynamic flows offer yet another dimension of control that emerge naturally
from the interactions between particles and fluid in colloidal
matter~\cite{Brandner2019,RevModPhys.93.025008}. Active colloidal
systems show nonequilibrium self-organization with complexity rivaling
that of biological systems such as living cells, bacterial baths, and
animal flocks~\cite{CollardGrosjeanVandewalle2020,Vutukuri2020}. A
long-standing challenge in fluid mechanics and material science is to
solve the ``inverse" problem of creating a model colloidal system that
will self-assemble into a prescribed
structure~\cite{PhysRevLett.128.256102}. For example, the framework of
geometrical frustration, which has been used to explain disordered
systems, could instead be used to design new, ordered systems, through
specific choices for the shapes or interactions of the
particles~\cite{Manoharan2015_Science}.

>>>>

\section{Introduction}
% Put \label in argument of \section for cross-referencing
%\section{\label{}}
Janus particles are colloids whose surfaces 
%have different properties. For example, it is common for the surface of a Janus
%particle to be 
may be partly hydrophilic and hydrophobic (polar and non-polar).
More generally the surface of a Janus particle may have a spatial distribution of hydrophobicity/hydrophilicity.
In the absence of any imposed flow, Janus particles often self-assemble into
structures in a viscous solvent with tunable functions for biomedical engineering
applications~\cite{GheisariSahfieeAbbasiEtAl2021_DMR,
LiuYangHuangEtAl2016_Angew, LiWangYaoEtAl2019_Nanoscale, Bradley2016}.
Depending on the interactions between Janus particles (JPs) and the
surrounding viscous solvent, JPs self-assemble into oligomers of various
geometries and sizes~\cite{Bradley2017}.

When driven by an external flow, 
dynamic rearrangement of JPs emerges naturally from the interactions between particles and fluid in colloidal
matter~\cite{Brandner2019,RevModPhys.93.025008}. Such colloidal hydrodynamics belongs to a wide class of
nonequilibrium self-organization in physics, often with complexity and features similar to that of 
biological systems such as living cells, bacterial baths, and
animal flocks~\cite{CollardGrosjeanVandewalle2020,Vutukuri2020}. A
long-standing challenge in fluid mechanics and material science is to
solve the ``inverse" problem of creating a model colloidal system that
will self-assemble into a prescribed
structure~\cite{PhysRevLett.128.256102}. For example, the framework of
geometrical frustration, which has been used to explain disordered
systems, could instead be used to design new, ordered systems, through
specific choices for the shapes or interactions of the
particles~\cite{Manoharan2015_Science}.
